A Comparison of Graph Processing Systems

### 2020-08-24 documentation/paper/sections/overview/giraph.tex

Apache Giraph\cite{Giraph} is an iterative graph processing framework, built on top of Apache Hadoop. Because of this, expanding shared memory processing to a multi-node cluster is almost seamless.

Giraph is inspired by the Bulk Synchronous Parallel model of distributed computation introduced by Leslie Valiant\cite{BSPforGiraph}. Meaning that it is based on computation units that communicate using messages and are synchonized with barriers.

>>>>

Apache Giraph is an iterative graph processing framework, built on top of Apache Hadoop\cite{Giraph}. Hadoop as a large MapReduce infrastructure provides a reliable (fault tolerant) basis for large scale graph processing.
Because of the underlying Hadoop MapReduce infrastructure, expanding single-node processing to a multi-node cluster is almost seamless.

Giraph is based on computation units that communicate using messages and are synchonized with barriers.

### 2020-08-24 documentation/paper/sections/results/results.tex

\begin{enumerate}
	\item During setup of Gemini, we realized that the cloned repository contained several bugs, rendering the code as-is unable to perform any calculations. We had to fork and modify the source code. TODO(Was genau ging nicht, was haben wir geändert?)

	The repository with our changes can be found \href{https://github.com/jasc7636/GeminiGraph}{here}\footnote{\url{https://github.com/jasc7636/GeminiGraph}}.
	\item Furthermore, we would like to address the setup of Hadoop for Giraph. It requires multiple edits in \texttt{xml} files that aren't easily automized. This makes the setup rather time consuming, especially if reconfiguration is needed later on.
	\item Also in order for Giraph to run, several Java tasks have to be constantly running in the background. While we don't expect this to have a noticeable performance impact on other tasks, it is still not optimal.
	\item The Hadoop distributed file system (HDFS) ran us into disk space problems on multiple occasions. First, unless configured otherwise, the standard implementation replicates all data three times, distributed over all participating nodes. Second, deleting files on the HDFS does not immediately free up disk space because the files are moved to a \emph{recycling bin}-like location.

@@

\subsection{Pure Performance-Ergebnisse}

\subsection{Ergebnisse Calc time}
\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_calcTime.png}
	\caption{Calculation times for SSSP on a single node}
	\label{fig:singleNodeSSSP_calc}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_calcTime.png}
	\caption{Calculation times for BFS on a single node}
	\label{fig:singleNodeBFS_calc}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSPGaloisThreads.png}
	\caption{Calculation times of Galois' SSSP over the thread count}
	\label{fig:singleNodeSSSPGaloisThreads}
\end{figure}

\subsection{Ergebnisse exec time}
\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_execTime.png}
	\caption{Execution times for SSSP on a single node}
	\label{fig:singleNodeSSSP_exec}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
	\caption{Normalized Overhead SSSP single node}
	\label{fig:singleNodeSSSP_overheadNormalized}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_execTime.png}
	\caption{Execution times for BFS on a single node}
	\label{fig:singleNodeBFS_exec}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{../../plots/singleNodeBFS_overheadTimeNormalized.png}
	\caption{Normalized Overhead BFS single node}
	\label{fig:singleNodeBFS_overheadNormalized}
\end{figure}

>>>>

\begin{enumerate}
	\item During setup and benchmark of Gemini, we encountered several bugs in the cloned repository. These include non zero-terminated strings or even missing return statements.

	The errors rendered the code as-is unable to perform calculations, forcing us to fork the repository and modify the source code. A repository with our changes can be found \href{https://github.com/jasc7636/GeminiGraph}{here}\footnote{\url{https://github.com/jasc7636/GeminiGraph}}.

	\item Furthermore, we would like to address the setup of Hadoop for Giraph. It requires multiple edits in \texttt{xml} files that aren't easily automized. This makes the setup rather time consuming, especially if reconfiguration is needed later on.
	\item In order for Giraph to run, several Java tasks (the Hadoop infrastructure) have to be constantly running in the background. While we don't expect this to have a significant performance impact on other tasks, it is still suboptimal.
	%\item The Hadoop distributed file system (HDFS) ran us into disk space problems on multiple occasions. First, unless configured otherwise, the standard implementation replicates all data three times, distributed over all participating nodes. Second, deleting files on the HDFS does not immediately free up disk space because the files are moved to a \emph{recycling bin}-like location.

@@

\subsection{Single-source Shortest-paths}
\autoref{fig:singleNodeSSSP} shows the average calculation times (time without initialization overhead), execution time and the normalized overhead for SSSP on the different frameworks. In these figures, Galois with 96 threads is shown. We show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}[t!]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times for SSSP on a single node}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times for SSSP on a single node}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
		\caption{Overhead time (execution time - calculation time) normalized by the graph size in million edges}
		\label{fig:singleNodeSSSP_overheadNormalized}
	\end{subfigure}
	\caption{Average times on a single computation node, black bars represent one standard deviation in our testing.}
	\label{fig:singleNodeSSSP}
\end{figure*}

\subsection{Breadth-first search}
In these figures, Galois with 96 threads is shown. Again, we show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
		\caption{Calculation times for BFS on a single node}
		\label{fig:singleNodeBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_execTime.png}
		\caption{Execution times for BFS on a single node}
		\label{fig:singleNodeBFS_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_overheadTimeNormalized.png}
		\caption{Overhead time (execution time - calculation time) normalized by the graph size in million edges}
		\label{fig:singleNodeBFS_overheadNormalized}
	\end{subfigure}

	\caption{Average times on a single computation node, black bars represent one standard deviation in our testing}
\end{figure*}

\subsection{PageRank}

\subsection{Galois speedup}
\label{sec:galois_speedup}
For Galois we

\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSPGaloisThreads.png}
		\caption{Single-source Shortest-paths}
		\label{fig:singleNodeSSSPGaloisThreads}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFSGaloisThreads.png}
		\caption{Breadth-first search}
		\label{fig:singleNodeBFSGaloisThreads}
	\end{subfigure}
	\caption{Calculation time speedup with increasing thread count for Galois Single-source Shortest-paths and Breadth-first search algorithms.}
\end{figure}

\begin{figure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\columnwidth]{../../plots/singleNodePRPullGaloisThreads.png}
		\caption{PageRank Pull}
		\label{fig:singleNodePRPullGaloisThreads}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}
		\includegraphics[width=\columnwidth]{../../plots/singleNodePRPushGaloisThreads.png}
		\caption{PageRank Push}
		\label{fig:singleNodePRPushGaloisThreads}
	\end{subfigure}
	\caption{Calculation time speedup with increasing thread count for Galois PageRank Push and Pull algorithms.}
\end{figure}

\subsection{Execution times and overhead}

@@

@@
